### 2018-10-25 Sections/encrypted_cloud_quantum_computing.tex
Commands and defs

The difference between the two protocols lies in the treatment of algorithms. In homomorphic encryption, Alice provides only the data, whereas Bob provides the processing and the algorithm it implements (which \sihui{in some cases} he would also like to keep to himself). \sihui{When any circuit is allowed, the protocol is said to be a {\it fully} homomorphic encryption protocol (FHE). Otherwise, it is a somewhat-homomorphic encryption protocol. \sihui{Although homomorphic encryption protocols have been around for a few decades in the form of privacy homomorphisms \cite{Rivest1978}, classical FHE} has only been described very recently \cite{bib:gentry2009fully, bib:van2010fully}.} In blind computing, Alice provides both the algorithm \textit{and} the data, and wishes \textit{both} to remain secret. Both of these protocols seem like very challenging goals, yet significant developments have been made on both fronts \sihui{in the quantum world. Interestingly, there are no classical analogue for universal blind computation. Classical FHE will be discussed in the next subsection.}

In the usual circuit model, blind quantum computation has been shown to be viable, and optimal bounds derived. Equivalently, such protocols have been described in the cluster state model (Sec.~\ref{sec:CSQC}). For universal computation, such protocols necessarily require classical interaction between the client and host. However, it was shown that in some restricted (i.e non-universal) models for optical quantum computation, specifically \textsc{BosonSampling}, quantum walks and coherent state passive linear optics, non-interactive \sihui{(somewhat-)}homomorphic encryption may be implemented.

@@

\subsection{Classical computation} \index{Classical encrypted computation}
\comment{A universal QC can implement any classical algorithm. So QCs with homo/BQC give us the means by which to perform encrypted classical computations, bypassing limitations imposed by purely classical protocols.}
\sihui{[Comment: The polynomial hierarchy is not contained in BQP. In fact, NP-complete problems are not contained in BQP.]}

@@

\sihui{The first FHE scheme was reported in Gentry's seminal paper \cite{bib:gentry2009fully}. He showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a somewhat homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates. For a security parameter $\lambda$, Gentry's scheme has a $\widetilde{O}(\lambda^6)$ \footnote{The tilde in the big O notation means that we are ignoring logarithmic factors.} bit bound on complexity for refreshing a ciphertext corresponding to a 1-bit plaintext \cite{bib:Gentrythesis}. This was subsequently reduced to $\widetilde{O}(\lambda^{3.5})$ \cite{bib:Damien2010}, $\widetilde{O}(\lambda)$ \cite{bib:Brakerski2011}, and ${\rm polylog (\lambda)}$ for any width-$\Omega(\lambda)$ circuit with $t$ gates \cite{bib:Craig2012}. }

\sihui{A homomorphic encryption scheme is made up of four algorithms: a key generation algorithm, {\sc KeyGen}, an encryption algorithm, {\sc Encrypt}, an evaluation algorithm, {\sc Evaluate}, and a decryption algorithm, {\sc Decrypt}. The four algorithms have the following inputs and outputs:
\begin{itemize}
\item 	 {\sc KeyGen}$(\lambda)$: Takes as input a security parameter $\lambda$, and outputs a public key $pk$, and a secret key $sk$.
\item {\sc Encrypt}$(pk, \pi_i)$: Takes as input $pk$, and a plaintext $\pi_i$. It outputs a ciphertext $\psi_i$.
\item {\sc Evaluate}$(pk, C, \Psi)$: Takes as input $pk$, a permitted circuit $C$, and $\Psi=(\psi_1,\ldots, \psi_t)$. It outputs a ciphertext $\psi$.
\item {\sc Decrypt}$(sk,\psi)$: Takes as input $sk$, and $\psi$ and outputs $C(\pi_1,\ldots, \pi_t)$.
\end{itemize}
The computational complexity of all these algorithms must be polynomial in $\lambda$, and in the case of the evaluation algorithm, polynomial in the size of the evaluation circuit $C$. The condition that {\sc Decrypt}$(sk,\psi)$ outputs $C(\pi_1,\ldots, \pi_t)$ is a condition known as correctness which we require of the homomorphic encryption scheme. Furthermore, we also require ciphertext size and decryption time to be upper bounded by a function of the security parameter $\lambda$, independently of $C$. This last condition is known as compactness, and is necessary to exclude trivial schemes such as that which decrypts the ciphertexts first, and then apply $C$.}

\sihui{The specifics of these algorithm vary from scheme to scheme, and as is in the case of FHE, usually contains sub-algorithms within them. Making FHE practical is an active area of research. Much of the problem lies in the bootstrapping required in Gentry's scheme, and some of these efforts lies in reducing the overhead required in bootstrapping or removing the need for bootstrapping entirely. Although there exists a plethora of FHE schemes, they are based mainly on two types of problems in lattice-based cryptography: the Shortest Vector Problem (SVP), and Learning with Errors (LWE) Problem. Gentry's original FHE was based on SVP, but over time, the schemes have moved towards a LWE approach because they offer lower overhead and are conceptually simpler . An overview of advances, and applications of homomorphic encryption can be found in a recent review \cite{bib:Halevi2017}.}

>>>>

The difference between the two protocols lies in the treatment of algorithms. In homomorphic encryption, Alice provides only the data, whereas Bob provides the processing and the algorithm it implements (which \comment{in some cases} he would also like to keep to himself). \comment{When any circuit is allowed, the protocol is said to be a {\it fully} homomorphic encryption protocol (FHE). Otherwise, it is a somewhat-homomorphic encryption protocol. \comment{Although homomorphic encryption protocols have been around for a few decades in the form of privacy homomorphisms \cite{Rivest1978}, classical FHE} has only been described very recently \cite{bib:gentry2009fully, bib:van2010fully}.} In blind computing, Alice provides both the algorithm \textit{and} the data, and wishes \textit{both} to remain secret. Both of these protocols seem like very challenging goals, yet significant developments have been made on both fronts \comment{in the quantum world. Interestingly, there are no classical analogue for universal blind computation. Classical FHE will be discussed in the next subsection.}

In the usual circuit model, blind quantum computation has been shown to be viable, and optimal bounds derived. Equivalently, such protocols have been described in the cluster state model (Sec.~\ref{sec:CSQC}). For universal computation, such protocols necessarily require classical interaction between the client and host. However, it was shown that in some restricted (i.e non-universal) models for optical quantum computation, specifically \textsc{BosonSampling}, quantum walks and coherent state passive linear optics, non-interactive \comment{(somewhat-)}homomorphic encryption may be implemented.

@@

\subsection{Classical computation} \index{Classical encrypted computation}
\comment{A universal QC can implement any classical algorithm. So QCs with homo/BQC give us the means by which to perform encrypted classical computations, bypassing limitations imposed by purely classical protocols.}
\comment{[Comment: The polynomial hierarchy is not contained in BQP. In fact, NP-complete problems are not contained in BQP.]}

@@

\comment{The first FHE scheme was reported in Gentry's seminal paper \cite{bib:gentry2009fully}. He showed that if a homomorphic encryption scheme can evaluate its own decryption circuit, and also slightly augmented versions of it--a feature he calls {\it bootstrapping}, one can construct a FHE scheme from it. Then he constructed a somewhat homomorphic encryption protocol using ideal lattices, and via a clever transformation that decreases the complexity of its decryption circuit, showed that it is bootstrappable with respect to a universal set of gates. For a security parameter $\lambda$, Gentry's scheme has a $\widetilde{O}(\lambda^6)$ \footnote{The tilde in the big O notation means that we are ignoring logarithmic factors.} bit bound on complexity for refreshing a ciphertext corresponding to a 1-bit plaintext \cite{bib:Gentrythesis}. This was subsequently reduced to $\widetilde{O}(\lambda^{3.5})$ \cite{bib:Damien2010}, $\widetilde{O}(\lambda)$ \cite{bib:Brakerski2011}, and ${\rm polylog (\lambda)}$ for any width-$\Omega(\lambda)$ circuit with $t$ gates \cite{bib:Craig2012}. }

\comment{A homomorphic encryption scheme is made up of four algorithms: a key generation algorithm, {\sc KeyGen}, an encryption algorithm, {\sc Encrypt}, an evaluation algorithm, {\sc Evaluate}, and a decryption algorithm, {\sc Decrypt}. The four algorithms have the following inputs and outputs:
\begin{itemize}
\item 	 {\sc KeyGen}$(\lambda)$: Takes as input a security parameter $\lambda$, and outputs a public key $pk$, and a secret key $sk$.
\item {\sc Encrypt}$(pk, \pi_i)$: Takes as input $pk$, and a plaintext $\pi_i$. It outputs a ciphertext $\psi_i$.
\item {\sc Evaluate}$(pk, C, \Psi)$: Takes as input $pk$, a permitted circuit $C$, and $\Psi=(\psi_1,\ldots, \psi_t)$. It outputs a ciphertext $\psi$.
\item {\sc Decrypt}$(sk,\psi)$: Takes as input $sk$, and $\psi$ and outputs $C(\pi_1,\ldots, \pi_t)$.
\end{itemize}
The computational complexity of all these algorithms must be polynomial in $\lambda$, and in the case of the evaluation algorithm, polynomial in the size of the evaluation circuit $C$. The condition that {\sc Decrypt}$(sk,\psi)$ outputs $C(\pi_1,\ldots, \pi_t)$ is a condition known as correctness which we require of the homomorphic encryption scheme. Furthermore, we also require ciphertext size and decryption time to be upper bounded by a function of the security parameter $\lambda$, independently of $C$. This last condition is known as compactness, and is necessary to exclude trivial schemes such as that which decrypts the ciphertexts first, and then apply $C$.}

\comment{The specifics of these algorithm vary from scheme to scheme, and as is in the case of FHE, usually contains sub-algorithms within them. Making FHE practical is an active area of research. Much of the problem lies in the bootstrapping required in Gentry's scheme, and some of these efforts lies in reducing the overhead required in bootstrapping or removing the need for bootstrapping entirely. Although there exists a plethora of FHE schemes, they are based mainly on two types of problems in lattice-based cryptography: the Shortest Vector Problem (SVP), and Learning with Errors (LWE) Problem. Gentry's original FHE was based on SVP, but over time, the schemes have moved towards a LWE approach because they offer lower overhead and are conceptually simpler . An overview of advances, and applications of homomorphic encryption can be found in a recent review \cite{bib:Halevi2017}.}
